A Survey on Ordered Binary Decision Diagrams

### 2015-09-15 paper.tex
Revise ITE operator
Revise Garbage collection

This formulation is based upon the fact, that every node $n$ of an OBDD represents
a Boolean function and is denoted by a triple $(var(n), hi(n), lo(n))$.
%Brace et al.~\cite{BRACE90} called the variable associated with $n$ the
%\textit{top variable} of $n$.

@@

The first OBDD package containing kind of a garbage collection was the one
introduced by Brace, Bryant and Rudell~\cite{BRACE90}. The garbage collection was
based upon the reference counting technique, i.e. every node of the OBDD had a
reference count. This reference count represents two kinds of references, (1)
the number of other nodes and (2) the number of formulas referencing it, but does
not take references from the unique- and computed-table into account.

Today, garbage collecion is a well-known topic. It is used to free up unnecessary
allocated or unused memory. To accomplish this, the garbage collection has to know
about which parts of the memory are \textit{dead} and thus can be freed. A node
of an OBDD is called \textit{dead} if the reference count of it is equal to zero.
The reference count of a node $x$ is decremented every time a corresponding
formula is freed. If the reference count of $x$ reaches zero, the reference counts
of $lo(x)$ and $hi(x)$ are decremented recursively~\cite{BRACE90}.

@@

The garbage collection is executed whenever the load factor (the ratio between
number of keys stored and number of available bins) exceeds 4 after an insertion
and $10\%$ of all OBDD nodes are dead. A garbage collection run deletes all entries
in the computed-table referencing dead nodes, and frees all dead nodes. The sizes
of computed- as well as unique-table are increased if the garbage collection does
not find enough dead nodes. Another event invoking the garbage collection is the
memory overflow of computed- and unique-table, although, the $10\%$-threshold of
dead nodes is used again. In any other case, the garbage collection gives up (and,
of course, frees all intermediate nodes)~\cite{BRACE90}.

As stated by Brace et al.~\cite{BRACE90}, this provides effective memory usage
at very low run-time costs, i.e. $3-7\%$ of the total runtime. \tbr

>>>>

This formulation is based upon the fact, that every node $n$ of an OBDD represents
a Boolean function and is denoted by a triple $(var(n), hi(n), lo(n))$. $var(x)$
here denotes the top-most variable among the three OBDDs $x$, $h$ and $l$.
%Brace et al.~\cite{BRACE90} called the variable associated with $n$ the
%\textit{top variable} of $n$.

@@

The first OBDD package containing kind of a garbage collection was the one
introduced by Brace, Bryant and Rudell~\cite{BRACE90}. The garbage collection was
based upon the reference counting technique, i.e. every node of the OBDD has its own
reference count. This reference count represents two kinds of references, (1)
the number of other nodes and (2) the number of formulas referencing it, but does
not take references from the unique- and computed-table into account.

Today, garbage collecion is a well-known topic. It is used to free memory of
objects that are no longer in use. To accomplish this, the garbage collection has
to know which parts of the memory are \textit{dead} and thus can be freed. A node
of an OBDD is called \textit{dead} if the reference count of it is equal to zero.
The reference count of a node $x$ is decremented every time a corresponding
formula is freed. If the reference count of $x$ reaches zero, the reference counts
of $lo(x)$ and $hi(x)$ are decremented recursively~\cite{BRACE90}.

@@

The garbage collection is executed whenever the load factor (the ratio between
number of stored keys and number of available bins) exceeds 4 after an insertion,
and $10\%$ of all OBDD nodes are dead. A garbage collection run deletes all entries
in the computed-table referencing dead nodes, and frees all dead nodes. The sizes
of computed- as well as unique-table are increased if the garbage collection does
not find enough dead nodes. Another event invoking the garbage collection is the
memory overflow of computed- and unique-table, although, the $10\%$-threshold of
dead nodes is used here again. In any other case, the garbage collection gives up (and,
of course, frees all intermediate nodes)~\cite{BRACE90}.

As stated by Brace et al.~\cite{BRACE90}, this provides effective memory usage
at very low runtime costs, i.e. $3-7\%$ of the total runtime.
